Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2014-02-04 paper.tex
added bpsk crbs. qpsk is next.

Turbo synchrnoisation can require a large number of EM iterations.  For applications with low power receivers, such as sensor networks, the complexity of turbo sychronisation might be too great and computationally simple channel estimators are required.  For example, in practice it is common to rely on channel estimates obtained from pilot symbols alone.  In this case it is necessary that the number of pilots symbols is sufficiently large for channel estimates to be sufficiently accurate.  If more accuracy is required, then more pilots symbols must be used.  Our estimator provides a simple mechanism for increasing accuracy without increasing the number pilot symbols, but instead using a subset of the data symbols.  For computational complexity reasons it may not be desirable to use all of the existing data symbols for channel estimation.  This is easily possible with our estimator by choosing the indices in $D$ to correspond with the subset of the data symbols that are to be used.

>>>>

Turbo synchrnoisation can require a large number of EM iterations.  For applications with low power receivers, such as sensor networks, the complexity of turbo sychronisation might be too great and computationally simple channel estimators are required.  For example, in practice it is common to rely on channel estimates obtained from pilot symbols alone.  In this case the number of pilots symbols must be sufficiently large for channel estimates to be sufficiently accurate.  If more accuracy is required, then more pilots symbols must be used.  Our estimator provides a simple mechanism for increasing accuracy without increasing the number pilot symbols.  Instead, the pilots symbols and a subset of the data symbols can be jointly used for channel estimation.  %For computational complexity reasons it may not be desirable to use all of the existing data symbols for channel estimation.  This is easily possible with our estimator by choosing the indices in $D$ to correspond with the subset of the data symbols that are to be used.
